<h4>LRT Report for `r input$t1`.</h4>

LRT Results based on Total Events
`r prrtitle()`
`r helpText('Results sorted by LRR')`

```{r prr, fig.width=5, echo=FALSE}
kable(prrnohyper(), digits=2, escape=FALSE )
```

```{r cloudprr, fig.height=8, fig.width=8, echo=TRUE, fig.keep='last', error=FALSE, warning=FALSE}
cloudprr()
```

```{r textplot, fig.height=8, fig.width=8, echo=FALSE}
textplot()
```

<h5>Simulation Results for Event Based LRT</h5><br>
```{r simplot, fig.height=6, fig.width=8, echo=FALSE}
simplot()
```


<h5>Analyzed EventCounts for Drug</h5><br>
`r alldrugtextAnalyzedEventCountsforDrug()`
`r alldrugqueryAnalyzedEventCountsforDrug()`
`r titleAnalyzedEventCountsforDrug()`
`r queryAnalyzedEventCountsforDrug()`
```{r AnalyzedEventCountsforDrug, echo=FALSE}
kable(AnalyzedEventCountsforDrugnohyper(), escape=FALSE)
```

```{r cloudAnalyzedEventCountsforDrug, fig.height=8, fig.width=8, fig.keep='last', echo=FALSE}
cloudAnalyzedEventCountsforDrug()
```

<h5>Analyzed Event Counts for All Drugs</h5><br>
`r alltext()`
`r queryalltext()`
`r alltitle()`
```{r All, echo=FALSE}
kable(allnohyper(), escape=FALSE)
```

```{r cloudall, fig.height=8, fig.width=8, echo=FALSE, fig.keep='last'}
cloudall()
```